\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-16 system_overview.tex
review comments by David implemented

\section{System Overview}
The soft grasping manipulator shown in Figure \ref{fig:egg_approach_sequence} has six bidirectional segments with cylindrical cavities forming the arm and a single soft gripper with a pleated shape as the end effector. 
The independent pneumatic actuation of the unidirectional gripper and each bidirectional arm segment, is achieved through an array of 13 custom fluidic drive cylinders \cite{marchese2014design}.
%All 13 cavities of the manipulator are pneumatically controlled by fluidic drive cylinders \cite{marchese2014design} and move with minimal friction on a level plane.
An object of feasible size but unknown geometry is randomly placed within the reachable envelop of the manipulator.  
The location of the manipulator and the object is determined with an external localization system. 
The motion planning algorithm as well as the curvature controller run on the control computers and take the location information as input.
The curvature controller then provides continuous closed-loop adjustment of the fluidic drive cylinder array.

>>>>

\section{System Overview}
The soft grasping manipulator shown in Figure \ref{fig:egg_approach_sequence} has six bidirectional segments with cylindrical cavities forming the arm and a single soft gripper with a pleated shape (Figure~\ref{fig:design}) as the end effector. 
The independent pneumatic actuation of the unidirectional soft gripper and each bidirectional arm segment, is achieved through an array of 13 custom fluidic drive cylinders \cite{marchese2014design}.
%All 13 cavities of the manipulator are pneumatically controlled by fluidic drive cylinders \cite{marchese2014design} and move with minimal friction on a level plane.
An object of feasible size but unknown geometry is randomly placed within the reachable envelop of the manipulator.  
The location of the manipulator and the object is determined with an external localization system. 
The motion planning algorithm as well as the curvature controller run on the control computers and take the location information as input.
The curvature controller then provides continuous closed-loop adjustment of the fluidic drive cylinder array.
